---
title: "Run MKL benchmarks"
author: "Andrie de Vries"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Run MKL benchmarks}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

# Running the tests

The package allows you to run benchmark tests on several different installations of R on the same machine.

The benchmarks are an adaptation of [Simon Urbanek's benchmarks](http://r.research.att.com/benchmarks/R-benchmark-25.R), and have been included in the function `RevoMultiBenchmark()` in the `version.compare` package.

```{r}
library("version.compare")
library("knitr")
scale.factor <- 1.0
```

This vignette scales the test sets down to `r sprintf("%1.0f%%", 100*scale.factor)` of standard size, to speed up the process for sake of illustration. For a full-scale test, adjust the tests by setting `scale.factor <- 1`.

```{r benchmark, echo=TRUE}

r <- switch(Sys.info()[["sysname"]],
            Linux = {
              rscript <- findRscript()
              
              rv <- version.time(rscript, {
                as.character(getRversion())
              })
              idx <- which(unlist(rv$results) == "3.4.1")
              rscript[idx]
              
            },
            Windows = findRscript(version = "3.4.1.*x64"
            )
)
test.results <- RevoMultiBenchmark(rVersions = r, 
                                   threads = c(1, 4, 8), 
                                   scale.factor = scale.factor)
```

```{r compare-results, eval = FALSE}
kable(test.results)
plot(test.results, theme_size = 8, main = "Elapsed time")
```

```{r performance-speed-up, eval = FALSE}
kable(urbanekPerformance(test.results), digits = 2)
plot(urbanekPerformance(test.results), theme_size = 8, main = "Relative Performance")
```

# Compare results

## Elapsed time (seconds)

The package  captures the total elapsed time for each of the benchmark tests. This makes it easy to compare the total elapsed time (in seconds).


```{r compare-results, echo = FALSE, fig.width=6, fig.height=3, out.width="800px", dpi=1200, keep=TRUE}
```

## Relative performance

You may also want to compare relative performance. To do this, divide each column by the longest-running test. This means scaling is relative to the version of R that has the longest elapsed time.


```{r performance-speed-up, echo = FALSE, fig.width=6, fig.height=3, out.width="800px", dpi=1200}
```
